\documentclass[12pt,a4paper]{article}
\usepackage{amssymb,amsmath,latexsym}
\usepackage[utf8]{inputenc}
% \usepackage[czech]{babel}
\usepackage[T1]{fontenc}
\usepackage{hyperref}

\usepackage[top=2.5cm, left=1.5cm, text={18cm, 24cm}]{geometry}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

\renewcommand{\baselinestretch}{1.5} % 1.5 denotes double spacing. Changing it will change the spacing

\usepackage{listings}
\setlength{\parindent}{0in} 

\begin{document}
\title{\vspace{-2.0cm} Creating \texttt{pcb-tools} Haskell library 
				\\ \small{parsing Gerber RS-274X, Excellon and other Haskell tales}}
\author{Bc. Adam Lučanský}
\date{\today}
\maketitle
\abstract{This documents briefly explains grammar of the parsed languages, as well as the Abstract-Syntax-Tree emitted by the parser.}

\section{Introduction}
This project sets goal to initiate effort to create Haskell library supporting PCB manufacturing processes (up to certain use-cases) and sub-programs for specific tasks related to manufacturing/milling.

In the first phase of the project, modules parsing and interpreting \texttt{Gerber RS-274X} \footnote{\url{https://www.ucamco.com/files/downloads/file/81/the_gerber_file_format_specification.pdf}} (layer description) format as well as \texttt{Excellon} (drilling) were created.
Parsing is implemented by the Attoparsec LL($\infty$) parsec \footnote{\url{https://wiki.haskell.org/Parsec}} library. Interpretation is performed in State monad.

This shall be the base point for the further work.

Following sections introduce grammar of parsed/interpreted languages with examples.

\section{Gerber RS-274X}
Gerber RS-274X is a structured human-readable ASCII format describing vector graphics. Use-case for this format can be found in PCB manufacturing processes.

\newpage % hack-fix
\lstset{language=bash}
\lstset{frame=lines}
\lstset{caption={Example Gerber source file}}
\lstset{label={lst:gerber_example}}
\lstset{basicstyle=\footnotesize\ttfamily}
\begin{lstlisting}
%ADD10C,1.321*%
%ADD11OC8,1.321*%
%ADD12C,1.524*%
%ADD13C,1.270*%
D10*
X42164Y05283D02*
X42164Y06604D01*
X44704Y06604D02*
X44704Y05283D01*
X47244Y05283D02*
X47244Y06604D01*
X47244Y14224D02*
\end{lstlisting}

\subsection{Grammar}
\lstset{caption={Grammar rules of implemented Gerber parser in EBNF}}
\lstset{label={lst:gerber_ebnf}}
\lstset{basicstyle=\scriptsize\ttfamily}
\lstinputlisting{gerber.ebnf}

\subsection{AST}

\section{Excellon}
Excellon is a language used for defining drilling and slotting jobs for CNC machines. Although Excellon has no single official specification, syntax can be derived from outputs of CAM software (Eagle, KiCAD, Altium\dots).

\subsection{Grammar}

\subsection{AST}

\section{Graphical output}
Library \texttt{diagrams} \footnote{\url{https://archives.haskell.org/projects.haskell.org/diagrams/}} is used in order to render trails drawn by the Gerber interpreter.

\end{document}